---
title: "Two Parameters"
author: "Roshan Ranganathan"
format: html
execute: 
  echo: false
---

```{r}
#| message: FALSE
library(tidyverse)
library(primer.data)
library(brms)
library(tidybayes)
library(gtsummary)
```

```{r}
nhanes |> 
  filter(sex == "Male", age >= 18) |> 
  select(height) |> 
  drop_na() |>
  ggplot(aes(x = height))+
  geom_histogram(bins = 50) +
  labs(title = "Male Adult Height in the US in 2010",
  x = "Height (cm)",
  y = "Count",
  caption = "Source: National Health and Nutritional Examination Survey")

ch5 <- nhanes |>
  filter(sex == "Male", age >= 18) |>
  select(height) |>
  drop_na()
```

We refined the NHANES dataset to focus on adult males, visualized their height distribution, and estimated the likelihood of encountering a man taller than 180 cm to analyze height trends. Addressing Justice in data science, we ensured our models considered the Population Table, stability, representativeness, and unconfoundedness. We recognized that non-representativeness due to voluntary participation could affect results. Applying Courage, we developed and tested a linear model to estimate average height, validating our approach to ensure accurate insights.

```{r}
#| cache: TRUE
fit_male_height <- brm(formula = height ~ 1, data = ch5, family = gaussian(), silent = 2, refresh = 0, seed = 12)
```

```{r}
tbl_regression(fit_male_height, intercept = TRUE)
```

```{r}
#| label: plot
ndata <- tibble(.rows = 1)
fit_male_height |>
  add_predicted_draws(newdata = ndata) |> 
  ggplot(aes(x = .prediction)) +
    geom_histogram(aes(y = after_stat(count/sum(count))), bins = 100) +
    labs(title = "Posterior for Height of Random Male",
    subtitle = "Uncertainty for a single individual is much greater than for the expected value",
    x = "Height (cm)",
    y = "Probability",
    caption = "Data source: NHANES") + 
    scale_x_continuous(labels = scales::number_format()) +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1))
```

```{r}
fit_male_height |> 
  add_predicted_draws(newdata = ndata) |>
  mutate(tall = if_else(.prediction > 180, TRUE, FALSE)) |>
  summarize(odds = mean(tall))
```

